I have been extremely fortunate to receive the support and guidance of my supervisor, Dr. Xiaoqi Tan. He has been not only an academic advisor throughout my research, but also a mentor who has offered invaluable advice and encouragement in my career. I am grateful for the trust and freedom he has given me to explore my own research interests, while consistently providing key insights and thoughtful feedback. We have explored many exciting research directions together, and he has encouraged me to grow as an independent researcher. His unique perspective and research vision have greatly shaped my approach to research and continue to motivate me to pursue new ideas.

I would also like to thank the members of my thesis committee, Dr. Omid Ardakanian and Dr. James Wright. Together with many other faculty members in the department, they have inspired me through their passion for research and dedication to teaching.

Additionally, I am eternally grateful to my labmates, Faraz, Haoxin, Hossein, Yanzhao, and Ying, who made this rewarding journey all the more enjoyable. I also thank my mountain friends, Kinter and Sam, who accompanied me on many questionable adventures in the beautiful Canadian Rockies.

Most importantly, I extend my deepest gratitude to my family for their unwavering support and unconditional love. They made countless sacrifices and shouldered significant financial burdens to provide me with the best they could, all while supporting my choices and affording me the agency to pursue my dreams.

Lastly, I would like to thank Alberta Innovates and the Alberta Machine Intelligence Institute (Amii) for the resources and funding support that made this research possible.